\documentclass{newspaper1920}

\def\minipageheight{37}

\begin{document}

\begin{multicols}{3}

\headlineMain{Foreign Cables}

\input{articles/filler/foreign-cables/artist-divorced.tex}

\halfrule

\input{articles/filler/foreign-cables/gold-in-glacier.tex}

\halfrule

\input{articles/filler/foreign-cables/wrecked-train.tex}

\halfrule

\input{articles/filler/foreign-cables/prince-drove-truck.tex}

\halfrule

\input{articles/filler/foreign-cables/100-killed-in-battle.tex}

\halfrule

\input{articles/filler/foreign-cables/ignores-rebels.tex}

\fullrule

\input{articles/filler/brisbane-denies-marriage-rumors.tex}

\halfrule

\input{articles/filler/flashes-badge-at-hotel-pays-5-fine.tex}

\halfrule

\input{articles/campaign-2020-05/statue-donated-to-danvers-asylum.tex}

\columnbreak

\noindent
\begin{minipage}[t][\minipageheight\baselineskip]{2\columnwidth+1\columnsep}
\headlineMainSuper{Scotland destroyed}
\headlineMain{Earthquake shatters nation!}
\fancyrule
\vspace{-\baselineskip}\headlineMainSub{Hundreds of Thousands of Lives Lost in the Wreckage Caused by the Earthquake, Beyond All Accurate Counting or Identification.}
\vspace{-0.5\baselineskip}
\begin{multicols}{2}
WESTMINSTER (Reuters)---The earthquake which shook Scotland from
center to circumference a few minutes after 5 o'clock on the 10th of
July unleashed never-before-seen devastation, destroying most of the
cities and towns in the nation, surpassing even the California
Earthquake of 1906.  King George VI and Prime Minister David Lloyd
George have called upon the Royal Society to offer some explanation of
this catastrophe, as the British Isles are not known for such seismic
activity.

Scotland has been placed under military authority.  The Army Corps of
Royal Engineers, as well as drafted civil organisations, have been
tasked with clearing the wreckage in the major cities and saving as
many lives as can be found.  Due to the scale of the destruction, the
operation is predicted to last for months.  Military and government
authorities would not speculate on when Scotland will recover to its
previous state.

Though the cause of the earthquake is not yet known, geologists have
been able to predict its likely origin: the north west coast, a region
of large deep lochs, many of which have never been fully plumbed.
They theorise that the waters may have hidden some spot of geological
activity.  The Royal Navy have confirmed that the destruction in the
coastal Morar area is significant.

\headlineMainInner{Light Seen in Sky}

Sailors in the North Sea report seeing a brilliant blue light rising
into the sky minutes after the shaking began.  It is not yet known if
this has any connexion to the earthquake.  Some scientists have
speculated that the disturbance could have released trapped gasses,
which affected the sunlight in unusual ways.

\headlineMainInner{``Feral Men'' Attacking Troops}

Some dozens of people who felt the vibrations have been driven into
lunacy by the experience, acting in a way which some have described as
``feral.''  These afflicted individuals attack those around them, even
the troops trying to aid them, with reckless abandon.  The army are
trying to round up these people in order for them to receive care.

\end{multicols}

\vspace{-\baselineskip}\fullrule

\end{minipage}

\input{articles/masks-of-nyarlathotep/murderers-hanged.tex}

\fullrule

\input{articles/filler/new-guard-needed-for-leper-house.tex}

\halfrule

\input{articles/filler/alexandria-veterans-form-new-post.tex}

\begin{minipage}[t][\minipageheight\baselineskip]{2\columnwidth+1\columnsep}
\end{minipage}

\input{articles/filler/di-robilants-aid-dies-of-jungle-fever.tex}

\fullrule

\input{articles/filler/successful-entertainment-at-vaughville-school.tex}

\end{multicols}

\end{document}
