\documentclass{newspaper1920}

\begin{document}

\headlineMainSuper{Scotland destroyed}
\headlineMain{Earthquake shatters nation!}
\fancyrule
\vspace{-\baselineskip}\headlineMainSub{Hundreds of Thousands of Lives Lost in the Wreckage, Beyond All Accurate Counting or Identification.}
\vspace{-\baselineskip}
\begin{multicols}{3}
WESTMINSTER (Reuters)---The earthquake which shook Scotland from
center to circumference a few minutes after 5 o'clock on the XXth of
August unleashed never-before-seen devastation, destroying most of the
cities and towns in the nation, surpassing even the California
Earthquake of 1906.  King George VI and Prime Minister David Lloyd
George have called upon the Royal Society to offer some explanation of
this catastrophe, as the British Isles are not known for such seismic
activity.

Scotland has been placed under military authority.  The Army Corps of
Royal Engineers, as well as drafted civil organisations, have been
tasked with clearing the wreckage in the major cities and saving as
many lives as can be found.  Due to the scale of the destruction, the
operation is predicted to last for months.  Military and government
authorities would not speculate on when Scotland will recover to its
previous state.

Though the cause of the earthquake is not yet known, geologists have
been able to predict its likely origin: the north west coast, a region
of large deep lochs, many of which have never been fully plumbed.
They theorise that the waters may have hidden some spot of geological
activity.  The Royal Navy have confirmed that the destruction in the
coastal Morar area is significant.

\headlineMainInner{Light Seen in Sky}

Sailors in the North Sea report seeing a brilliant blue light rising
into the sky minutes after the shaking began.  It is not yet known if
this has any connexion to the earthquake.  Some scientists have
speculated that the disturbance could have released trapped gasses,
which affected the sunlight in unusual ways.

\headlineMainInner{``Feral Men'' Attacking Troops}

Some dozens of people who felt the vibrations have been driven into
lunacy by the experience, acting in a way which some have described as
``feral.''  These afflicted individuals attack those around them, even
the troops trying to aid them, with reckless abandon.  The army are
trying to round up these people in order for them to receive care.

\vfill
\headlineMainInner{\scshape Continued on page 2}

\end{multicols}

\vspace{-\baselineskip}\fullrule
\vspace{-\baselineskip}

\begin{multicols}{3}

\headlineMain{Di Robilant's Aide Dies of Jungle Fever}
\headlineMainSub{Italian Aviator Recovering}

SAO PAULO (Reuters)---A telegram received at Sao Paulo late today
advised the Italian Consul that Mauranta Quarenta, mechanic of Count
di Robilant's plane, died at San José this morning from injuries and
exhaustion.  Count di Robilant, occupying the next bed, when in formed
of Signor Quarenta's death shortly before noon, at first refused to
believe it.  Later he developed a high fever, causing considerable
alarm.  The hospital doctors now fear di Robilant may be suffering
from a tropical fever contracted during his eighteen days of
wandering, after the crash of his plane.

The Italian Consul at Sao Paulo informed Signor Quarenta's family,
living at Rio de Janeiro, of his death and the Italian Government will
transport the family to Italy.

Count di Robilant is unable to see visitors and the hospital doctors
here advised the Vice Consul at Sao Paulo that he will be transported
tomorrow morning to Assis, where better medical assistance is
obtainable.  He is believed to be out of danger, but requires special
treatment.

Signor Quarenta died as the result of yellow fever contracted on the
tortuous walk through dense forests, it is reported.  Count di
Robilant, although also affected, is expected to regain his health
soon.

\fullrule

\headlineMain{Murderers Hanged}

NAIROBI (Reuters)---Five Nandi tribesmen, convicted ringleaders of
the vicious Carlyle Expedition massacre, were executed this morning
after a short, expertly-conducted trial.

To the end, the tribesmen steadfastly refused to reveal why they had
slaughtered Mr. Carlyle and his companions.  Mr. Harvis, acting for
the Colony, cleverly implied throughout the trial that the massacre
was racial in motivation, and that the fair-skinned victims were
subject to the most savage treatment, preventing all but the most
preliminary identification of the remains.

Miss Erica Carlyle, defeated in her efforts to rescue her brother,
left several weeks ago, but is surely comforted now the triumph of
justice.

\headlineMain{Foreign Cables}

\headlineSmall{Artist Divorced}

PARIS, August XX (A.~P.)---Mrs.~Lucile Wolfe Burton was granted a
divorce today from William O.\ Burton, American portrait painter, now
living in Paris.

\halfrule

\headlineSmall{Gold in Glacier}

STOCKHOLM, August XX (A.~P.)---Norwegians may seek unknown land, but
some Swede engineers have found rich gold, silver and copper deposits
in an arctic glacier, using new electrical prospecting apparatus.

\halfrule

\headlineSmall{Wrecked Train}

MEXICO CITY, August XX (A.~P.)---The train which was wrecked near
Pachuca was carrying troops from Pahuca to Ixmiquilpan.  Ten men were
reported killed and 30 injured.  A military relief train was sent to
the scene.

\halfrule

\headlineSmall{Prince Drove Truck}

LONDON, August XX (A.~P.)---The prince of Wales is becoming a regular
Harun Al Raschid.  It develops that during the strike he drove a motor
truck and helped distribute milk to the poor.

\halfrule

\headlineSmall{100 Killed in Battle}

TANGIER, Morocco, August XX (A.~P.)---More than a hundred members of
the Spanish foreign legion are reported to have been killed and a
large number wounded in fighting at Rio Martin, near Tetuan.  Another
party numbering 360 persons are reported to have been surrounded in a
ravine by the tribesmen, all being captured or killed.

\halfrule

\headlineSmall{Ignores Rebels}

MANAGUCA, Nigaragua, August XX (A.~P.)---The revolutionary governor at
Bluefields has called upon W.~J.~Crampton, American collector of
customs there, to deliver the customs revenue to him.  The collector
refused and has requested protection for himself and his staff against
the rebels.

\fullrule

\headline{Brisbane Denies Marriage Rumors}

Mr.~Luther Brisbane, proprietor of Arkham's own Brisbane Brick Works,
today said there was ``absolutely nothing'' in rumors that he was soon
to be married to Mrs.~Adolph Spreckles of San Francisco, widow of the
nationally known sugar magnate.

\halfrule

\headline{Statue Donated to Danvers Asylum}

The Danvers State Asylum has received an anonymous donation of a
statue of Dr.~Shine, who made the facility into a model center for
care.  Dr.~Berger, the current superintendent, is pleased with the
gift, but confesses to some perplexity over the identity of the donor.

Dr.~Shine was superintendent of Danvers State Asylum from 1890 to
1915.  Prior to his arrival, the asylum had suffered from a poor
reputation and staff morale was low.  Patient accident and mortality
rates were among the highest in the country.

\halfrule

\headline{New Guard Needed for Leper House}

The District Health Department wants another guard for Willard
Centlivre and Charles H. Young, held at the leper house, until the
Public Health Service can take them over.

Someone is needed to relieve the guard now on duty at the leper house.
The department needs a man who can give approximately eight hours a
day, one day a week, for \$3 a day, preferable a man who has regular
employment at night.

\halfrule

\headline{Flashes Badge at Hotel, Pays \$5 Fine}

Flashing a badge that looked like that worn by policemen, Roman
Struck, 39 years old, 530 Powder Mill st., threatened the owners of a
hotel at Gedney and Armitage st.\ with arrest.  The sight of two
policemen, who were called, induced Struck to step into his more
accustomed role of a civilian.  When questioned by police as to why he
made the impersonation, he replied, ``I thought it would be fun.''

In district court today he was fined \$5 on charge of being drunk.

\halfrule

\headline{Successful Entertainment at Vaughnville~School}

One of the enjoyable social features of the Vaghnville community was
the entertainment given by the school at the new building.  There was
not a single hitch in the execution of the program from the beginning
to the finis.  Each child did his part remarkably well, especially
those beginners, who successfully dramatized the nursery rhyme of
Lucky Locket.  The play, ``Mother Goose Up to Date,'' was a great
success.

\end{multicols}

\end{document}
